---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse=TRUE, comment="##", fig.retina=2, fig.path = "README_figs/README-")
```

<b> PRELIMINARY </b> package containing several function and themes for `ggplot2` 

# Installation
You can directly install this package from Github 
```{r, eval = FALSE}
devtools::install_github("TIvanDijk/TivD")
```
To replicate the output of this markdown file, you'll need at least the following packages
```{r message = FALSE, warning = FALSE}
library(dplyr)
library(TivD)
library(ggplot2)
```

# Maps
For illustration purposes, we create a random dataset containing the municipality, associated province and some random count value.  

```{r}
library(TivD)

df = cbind(GPdata[, c('gem', 'prov')], count = rpois(352, 100))
head(df)
```


To plot the counts per Dutch municipality, you can use the `NLDgem` function. 
```{r}
NLDgem(df[, c('gem', 'count')], title = 'Random Poisson Values', varname = 'count')
```

To plot the counts per Dutch province, you can use the `NLDprov` function. I first summarise the counts across the province to get the dataset in the appropriate format. 
```{r}
df.prov <- dplyr::summarise( group_by(df, prov), count = sum(count))
NLDprov(df.prov, title = 'Sum of Poisson', varname = 'count')
```

# Themes
To illustrate the themes, consider the following simple plot
```{r}
p <- ggplot(data.frame(x = -5:5), aes( x = x)) +
  stat_function(aes(color = 'line 1'), fun = function(x) sin(x), size = 1.1) +
  stat_function(aes(color = 'line 2'), fun = function(x) cos(x), size = 1.1) +
  labs(title = 'Two Interesting Lines', subtitle = 'notice the alternating pattern',
       caption = 'source: high school mathematics')
```

### Notepad (`theme_notepad`)
```{r}
p + theme_notepad()
```

### Grey (`theme_newgrey`)
```{r}
p + theme_newgrey()
```

# Other

- setwd_here()
- GPdata
- clean()
